### 2023-04-20 chapter2/chapter2.tex
Expanded first section of results in full paragraph
Added first section of results

\section{Results}
% RESULTS
% I. Identification and filtering of IDRs
%     A. From a set of over 8,500 alignments of single copy orthologs from the genomes of up to 33 species in the \textit{Drosophila} genus, we identified X regions with high levels of inferred disorder using the predictor AUCPreD. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of Y regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and the phylogenetic diversity. In the subsequent discussion, we refer to these filtered sets as the ``disorder'' and ``order'' regions, respectively. The disorder
%     B. Some notes about the length distributions and other basic statistics
%
% II. Disorder regions have distinct patterns of residue substitution
%     A. To gain a global view of substitution patterns of amino acid residues in disorder and order regions, we fit amino acid substitution models to meta-alignments sampled from the respective sets of filtered regions.
%     B. Substitution models are parameterized in terms of the rates of change from one residue to another.
%         1. The rates are not necessarily equal between for a given pair of residues when the initial and target states are swapped.
%         2. For example, the rate of change of valine to tryptophan can be distinct from that of tryptophan to valine.
%         3. In practice, substitution models are typically constrained to fulfill a condition called time-reversibility, as this converts a difficult multivariate optimization of the tree's branch lengths into a series of simpler univariate optimizations~\cite{Felsenstein1981}. Therefore, the models are parameterized in terms of a frequency vector, $\mathbm{pi}$, and an exchangeability matrix, $S$. The frequency vector determines the model's expected residue frequencies at equilibrium, meaning all sequences eventually approach this distribution, no matter their initial composition. The exchangeability matrix is symmetric ($s_{ij} = s_{ji}$) and encodes the propensity for two residues to interconvert. Because the rate of change from residue $i$ to residue $j$ is given by $r_{ij} = s_{ij}\pi_{j}$, higher exchangeability coefficients yield higher rates of conversion. Thus, exchangeability coefficients are frequently interpreted as a measure of biochemical similarity between residues.
%     C. To highlight the differences in patterns of residue substitution between the disorder and order regions, the parameters in each model are directly compared in Fig.~\ref{fig:substitution}.
%         1. The disorder regions show an enrichment of "disorder-promoting" residues such as serine, proline, and alanine, and a depletion of hydrophobic and bulky residues such as trytophan and phenylalanine (Fig.~\ref{fig:substitution}A).
%         2. Overall, the exchangeability matrices fit to the disorder and order regions are similar in their overall pattern of high and low coefficients (Fig.~\ref{fig:substitution}B-C). However, the log ratios of the disorder to the order exchangeability coefficients show clear trends within and between the disorder-enriched and -depleted residues. In disorder regions, disorder-enriched residues are less exchangeable with each other, whereas disorder-depleted residues are more exchangeable with each other and with disorder-enriched residues (Fig.~\ref{fig:substitution}D).

>>>>

\section{Results}
\subsection{IDRs are shorter and more divergent than non-disordered regions}
We identified regions with high levels of inferred intrinsic disorder in over 8,500 alignments of single copy orthologs from 33 species in the \textit{Drosophila} genus using the disorder predictor AUCPreD~\cite{Wang2016}. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and their phylogenetic diversity, which yielded 11,445 and 14,927 regions, respectively, from 8,466 unique alignments. In the subsequent discussion, we refer to these sets as the ``disorder'' and ``order'' regions, respectively. To investigate the broad differences in basic sequence statistics between the two region sets, we first generated histograms from the average length of each region (Fig.~\ref{sfig:regions}). Although both distributions span several orders of magnitude, the order regions are generally longer than the disorder regions, with means of 105 and 245 residues, respectively. We then quantified the sequence divergence in each region by fitting phylogenetic trees to the alignments using amino acid and indel substitution models. The average rates of substitution are significantly larger in the disorder regions, demonstrating that while both sets contain conserved and divergent regions, IDRs are enriched in more rapidly evolving sequences (Fig.~\ref{sfig:regions}).
%
% II. Disorder regions have distinct patterns of residue substitution
%     A. To gain a global view of substitution patterns of amino acid residues in disorder and order regions, we fit amino acid substitution models to meta-alignments sampled from the respective sets of filtered regions.
%     B. Substitution models are parameterized in terms of the rates of change from one residue to another.
%         1. The rates are not necessarily equal between for a given pair of residues when the initial and target states are swapped.
%         2. For example, the rate of change of valine to tryptophan can be distinct from that of tryptophan to valine.
%         3. In practice, substitution models are typically constrained to fulfill a condition called time-reversibility, as this converts a difficult multivariate optimization of the tree's branch lengths into a series of simpler univariate optimizations~\cite{Felsenstein1981}. Therefore, the models are parameterized in terms of a frequency vector, $\mathbm{pi}$, and an exchangeability matrix, $S$. The frequency vector determines the model's expected residue frequencies at equilibrium, meaning all sequences eventually approach this distribution, no matter their initial composition. The exchangeability matrix is symmetric ($s_{ij} = s_{ji}$) and encodes the propensity for two residues to interconvert. Because the rate of change from residue $i$ to residue $j$ is given by $r_{ij} = s_{ij}\pi_{j}$, higher exchangeability coefficients yield higher rates of conversion. Thus, exchangeability coefficients are frequently interpreted as a measure of biochemical similarity between residues.
%     C. To highlight the differences in patterns of residue substitution between the disorder and order regions, the parameters in each model are directly compared in Fig.~\ref{fig:substitution}.
%         1. The disorder regions show an enrichment of "disorder-promoting" residues such as serine, proline, and alanine, and a depletion of hydrophobic and bulky residues such as trytophan and phenylalanine (Fig.~\ref{fig:substitution}A).
%         2. Overall, the exchangeability matrices fit to the disorder and order regions are similar in their overall pattern of high and low coefficients (Fig.~\ref{fig:substitution}B-C). However, the log ratios of the disorder to the order exchangeability coefficients show clear trends within and between the disorder-enriched and -depleted residues. In disorder regions, disorder-enriched residues are less exchangeable with each other, whereas disorder-depleted residues are more exchangeable with each other and with disorder-enriched residues (Fig.~\ref{fig:substitution}D).
